\section{Anticipated results}
\label{sec:results}

I anticipate initial difficulty in getting the prep to work properly, and thus will spend some portion of the Fall term on portions of the pilot study involving surgery and open loop testing. As protocols become improved, I will then think about implementing closed loop control from offboard, via a web cam and code, to replace the human steering the cockroach and achieve an autonomous, cockroach-in-the-loop system.  By measuring the time, current, and angles of turn throughout different maneuvers, I can quantify the directional and speed behavior of the cockroach. Using this relationship between applied current and speed or direction, I can achieve full remote control over the cockroach's movement. 

\subsection{Cockroach kinematics under natural/free-running versus stimulated}
One set of results I hope to look at closely are the running kinematics of an intact, natural, free-running cockroach versus one that is stimulated. To gater this data, I will consider use of a high speed camera filming from above, and either manual digitization using \lstinline{DLTdv8} (\url{http://biomech.web.unc.edu/dltdv/}) or some sort of automatic machine-vision enabled solution. I will also consider addition of accelerometers to the instrumentation on the roach. Automatic solutions are preferred as they would be the necessary for developing closed-loop control from an offboard controller. 

\subsection{Closed-loop performance}
It is unknown if I will reach closed-loop control in the fall term but it is a goal for the spring. Using what I learn, I may be able to have a controller off board steer the cockroach using a variety of methods. This necessarily would draw from a model of the open loop ahead running dynamics of a cockroach. 

\subsection{Other locomotion measures}
Aside from being able to steer a prescribed course or route, cockroaches are notable for their ability to traverse gaps and obstacles with very little loss in forward speed. Such abilities are desireable for a RoboRoach, so I would like to know if the backpack and sensors or if use of electrical stimulation compromises these other abilities. 


 